Benchmarking KiCS2

### 2014-10-07 benchmarks/benchmark_papers/kics2/bench_kics2.tex
benchmark paper corrected
Parallel search benchmarks added.
Benchmarks: MCC handling improved, nondet benchmarks refined

@@

\begin{center}
%\runcurry{mainBench (MCC:PAKCS:kics2Systems) detBench}
\end{center}

@@

The following benchmark programs contain non-deterministic operations
or free variables. We evaluate the computation of a
first solution/value via DFS in PAKCS vs. KiCS2:

\begin{center}
%\runcurry{mainBench [PAKCS, KiCS2 ""] nondetBenchDFS}
\end{center}

@@

\begin{center}
%\runcurry{mainBench kics2Systems nondetBench}
\end{center}

@@

\begin{center}
%\runcurry{mainBench kics2Systems encapsBench}
\end{center}

>>>>

\setlength{\parindent}{0ex}

@@

\begin{center}
\runcurry{mainBench (MCC:PAKCS:kics2Systems) detBench}
\end{center}

@@

The following benchmark programs contain non-deterministic operations
or free variables. We evaluate the computation of all
solutions/values via DFS in various Curry systems:

\begin{center}
\runcurry{mainBench [PAKCS, MCC, KiCS2 ""] nondetBenchDFS}
\end{center}

These benchmarks contain functional patterns which are not supported in MCC:

\begin{center}
\runcurry{mainBench [PAKCS, KiCS2 ""] funpatBenchDFS}
\end{center}

@@

The following benchmark programs compare various search strategies
as they are supported in KiCS2.

The first set of benchmarks computes all solutions/values:

\begin{center}
\runcurry{mainBench kics2Systems nondetBench}
\end{center}

The following benchmarks computes the first solution/value
only (since the search space is infinite):

\begin{center}
\runcurry{mainBench kics2Systems nondetBenchFirst}
\end{center}

\subsection{Parallel Non-deterministic Benchmarks}

\begin{center}
\runcurry{mainParBench (KiCS2 "") parSearchBench}
\end{center}

@@

\begin{center}
\runcurry{mainBench kics2Systems encapsBench}
\end{center}
